---
title: "Lecture 11"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:
```{r}
library(bio3d)
```

# Download some example PDB files 
```{r}
ids <- c("1TND_B","1AGR_A", "1TAG_A","1GG2_A","1KJY_A","4G5Q_A")
files <- get.pdb(ids, split = TRUE)
```
# Extract and align the chains we are interested in & print to screen a summary of the 'pdbs' object
```{r}
pdbs <- pdbaln(files, fit = TRUE)
pdbs
```

# Access the first 5 rows, and 8 columns 
```{r}
pdbs$ali[1:5, 1:8]
```
# Associated residues numbers 
```{r}
pdbs$resno[1:5, 1:8]
```

#Inspect alignment for gaps, indices of non-gap columns, & access non-gap columns
```{r}
gaps <- gap.inspect(pdbs$ali)   
head(gaps$f.inds) 
pdbs$ali[, gaps$f.inds]
```
#calculate sequence identity
```{r}
seqidentity(pdbs)
```

